\LARGE \bf A Pipeline for Assembling Collision and Near-Collision Dashcam Footage Datasets

### 2021-03-28 paper.tex
revive anonymization

% HAS BEEN REMOVED BECAUSE NOT FUNCTIONAL
%\subsection{Video Preprocessing}
%\subsection{Automatic Annotation}
%\subsection{Object Detection \& Tracking}
%\todo{Automated object detection not used right now?}
%\subsection{Anonymization}
%An important facet of automobile data aggregation is in eliminating biases and protecting the identities of depicted individuals. Consequently, our pipeline contains a post-processing stage in which we apply blurring masks to anonymize any personally identifiable information. Specifically, we provide two executors to perform these anonymization tasks: \texttt{FaceBlurrer}, which blurs faces and \texttt{LicensePlateBlurrer} which blurs license plates. Both of these executors are powered by pre-trained machine learning models which detect regions containing personally identifiable information. Specifically, for  \texttt{FaceBlurrer}, we use a MobileNet Single Shot MultiBox Detector (TODO: cite https://github.com/yeephycho/tensorflow-face-detection) and for \texttt{LicensePlateBlurrer} we use a Convolutional Neural Network (TODO: cite http://sergiomsilva.com/pubs/alpr-unconstrained/).
%
%This software module is encapsulated as a library and can be reused by importing our \texttt{anonymization} package as a dependency. The accuracy, amount and type of blurring applied can be tweaked using the API exposed by the \texttt{anonymization} package.

>>>>

%HAS BEEN REMOVED BECAUSE NOT FUNCTIONAL
%\subsection{Video Preprocessing}
%\subsection{Automatic Annotation}
%\subsection{Object Detection \& Tracking}
%\todo{Automated object detection not used right now?}
\subsection{Anonymization}
An important facet of automobile data aggregation is in eliminating biases and protecting the identities of depicted individuals. Consequently, our pipeline contains a post-processing stage in which we apply blurring masks to anonymize any personally identifiable information. Specifically, we provide the executor \texttt{FaceBlurrer}, which blurs faces. This executor first uses a MobileNet Single Shot MultiBox Detector \cite{yixuan_h_y_hu_2021_4642275} trained on the WIDERFACE dataset \cite{yang2016wider} to obtain the bounding boxes of all visibly identifiable individuals' faces at each frame of a given video and then applies a blurring mask over each bounding box.

This software module is encapsulated as a library and can be reused by importing our \texttt{anonymization} package. The accuracy, amount and type of blurring applied can be tweaked using the API exposed by the \texttt{anonymization} package.
